DATA 621 Homework #4

### 2019-11-15 hw4/HW4.Rmd
Work arround PR 21

model_results <- evaluate_model(model, test)
```

>>>>

model_results <- evaluate_model(model, test)
```
```{r}
# Evaluating the model
eval <- data.frame(actual = test$TARGET_FLAG, predicted = predict(model,newdata=test,type="response"), prob = 
predict(model,newdata=test,type="response"))

pred <- prediction(eval$predicted, eval$actual)
auc <- performance(pred, measure = "auc")@y.values[[1]]
perf <- performance(pred,"tpr","fpr")
plot(perf,main="ROC Curve", sub=paste0("AUC: ",round(auc,3)))
```

## Model Creation - Linear

First we need to remove the zero values from our train and test sets, as we are only interested in cases where there was an accident claim.

```{r}
train <- train %>% filter(TARGET_AMT > 0)
test <- test %>% filter(TARGET_AMT > 0)
```

As with the logistic model, we start with a baseline model using the `BLUEBOOK` variable as the sole predictor. All other models will need to beat this baseline.

```{r, null_prefix = TRUE, comment=NA}

baseline_model <- lm(TARGET_AMT ~ BLUEBOOK, train)
summary(baseline_model)
```

This model is rather poor, though the predictor is statistically significant in the model. We can build on this model and see if we can build a more robust version.

### Car Model

Here we look at the type of car the person drives, it's age, and how it is used.

```{r}
car_model <- lm(TARGET_AMT ~ CAR_AGE + CAR_TYPE + CAR_USE, data = train)
summary(car_model)
```

Here we see that none of these predictors are significant in this model. In fact, taken one at a time, none are significant individually either.

### Personal Model

Here we use variables pertaining to the driver's personal life: family, income, driving record, and work.

```{r}
personal_model <- lm(TARGET_AMT ~ MSTATUS + INCOME + KIDSDRIV +
                       HOME_VAL + AGE + REVOKED + MVR_PTS +
                       HOMEKIDS, data= train)

summary(personal_model)
```

Again, we see a very poor model. No variables are statistically significant here (though 2 are close).

### Additive Model

Here we start with `BLUEBOOK` from the baseline model and add to it until we get a decent model.

```{r}
add_model <- lm(TARGET_AMT ~ BLUEBOOK + CLM_FREQ, data = train)

summary(add_model)
```
